```{r}
```{r}
ToPlotOrd=sort(ToPlot)
###

tableFreq[order(-tableFreq$pct),]

par(mgp=c(1,0.5,0))
location=barplot(ToPlotOrd,
         col = 'gray',
         border=NA,
         main=titleText,
         xlim=c(0,50), 
         xlab = '(in %)',
         horiz = T,
         cex.names = 0.7,
         cex.lab=0.6,
         xaxt="n") 

text(x=ToPlotOrd,y=location,labels=plotLabels,pos = 2,cex = 0.7) 
title(sub=sourceText, adj=0,cex.sub=0.7,line = 3) 

abline(v=25,lty=3,lwd=3)

xtick<-c(0,10,25,40,50)
axis(side=1, at=xtick, labels = xtick,cex.axis=0.8)
#Exercise1
```


```{r}
ase = ggplot(tableFreq, aes(x=offense,pct)) 
lolliplot1=base + geom_segment(aes(y = 0, 
                                   x = offense, 
                                   yend = pct, 
                                   xend = offense), color = "grey50") 
lolliplot1 + geom_point()
#Exercise2
```


```{r}
ordLabels= levels(eduwa$High.Grade)
box2 = box1 + scale_y_continuous(labels=ordLabels,breaks=1:15)
box2
#Exercise3
```

```{r}
base= ggplot(eduwa3,aes(x = Free.Lunch))  
h1= base + geom_histogram()
h1 
#Exercise4
```

```{r}
mvDense=density(meanValues)
hist(meanValues)
plot(mvDense,main="Title",col='black',xlab=NA,)

abline(v=mean(meanValues),lty=3,lwd=3,col='blue') #mean
abline(v=median(meanValues),lty=3,lwd=3,col='red')#median
legend(x="right",
       legend=c('mean','median'),
       fill = c('blue','red'),bty = 'n') #no box in the legend
#Exercise 5
```

